Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-11-29 paper.tex
Add modified plots and insert them in document.

\usepackage[pdftex]{graphicx}
\usepackage{tikz}

@@

>>>>

\usepackage[pdftex]{graphicx}
\usepackage{epstopdf}
\usepackage{tikz}

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.8\linewidth]{plots/rrt-it.eps}
\caption{Number of RRT iterations $it$ for the floating objects and the
  shelf scenarios, using two variants of RRT. Mean $\overline{it}$,
  standard deviation $\sigma_{it}$, minimum and maximum values are
  represented.}
\label{fig:rrt-it}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=0.8\linewidth]{plots/rrt-t.eps}
\caption{RRT computation time $t$ for the floating objects and the shelf
  scenarios, using two variants of RRT. Mean $\overline{t}$, standard
  deviation $\sigma_{t}$, minimum and maximum values are represented.}
\label{fig:rrt-t}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[width=0.8\linewidth]{plots/rrt-n.eps}
\caption{Number of tree nodes $n$ for the floating objects and the
  shelf scenarios, using two variants of RRT. Mean $\overline{n}$,
  standard deviation $\sigma_{n}$, minimum and maximum values are
  represented.}
\label{fig:rrt-n}
\end{figure}
